UGrade: Autograder for Competitive Programming Using Contestant PC as Worker

### 2019-11-02 src/paper.tex
remove we

Currently, almost every competitive programming competition uses online judge system to support the competition and use many computers to run autograder in order to improve grading performance. Every computer that runs autograder is called a worker. Grading performance is defined as the number of submissions graded in a certain amount of time. Even though autograder deployed in many computers, the grading performance often not enough to evaluate contestant solutions in real-time because the number of contestants is increasing. Furthermore, the number of computers to deploy autograder affect the procurement cost that juries need to be incurred. Therefore, a new grading system is needed to increase grading performance without increasing procurement cost that needs to be incurred.

@@

We need to consider the security aspect when developing an autograding system. Competitive programming contestants might submit source code that contains dangerous code. According to \cite{wasikojsurvey}, there are several attacks that can be made by contestants, such as submitting compile bomb code, submitting code that destroys the autograder environment and submitting code that access forbidden computer's resource. In order to prevent such things, an autograding system must execute contestant's code in an isolated environment called sandbox.

There are several ways to create an isolated environment such as using virtual machine and containerization. By using a virtual machine, one can create an isolated operating system inside the host computer. The virtual machine uses the hypervisor to emulate computer hardware and run its own operating system. In Linux based operating system, there is a feature called KVM that makes it possible to create hypervisor as a process in Linux \cite{wfeltervmcontainer}. We can use a virtual machine to isolate the execution of contestant's code. However, by using the virtual machine, we need to boot a new operating system each time we evaluate contestant's submission. This booting process takes so much computer's resource and reduces grading performance.

Another way to create an isolated environment is by using a container. A container is different from a virtual machine. A container gives isolation in software level without hypervisor \cite{merkeldocker}. By using a container, we can isolate process execution without booting a new operating system. The container works by using some Linux features such as chroot, namespace and cgroup. By using chroot, we can isolate the filesystem of Linux process \cite{lessardchroot}. The container uses a Linux feature called cgroup to limit process resources. By using cgroup, we can limit memory usage, CPU usage and disk IO usage of running process \cite{wfeltervmcontainer}. In order to hide other processes, user, and network from a running process, the container uses a Linux feature called namespace. By using a namespace, we can isolate a Linux process from other processes, so the running process not aware of the existence of other processes. Instead of a virtual machine, most of the autograding systems use container to isolate the grading process. This method is used because it is lighter and faster than the virtual machine.

@@

Contestants' computers have different specification and performance. We cannot force the contestants to have an identical computer. Thus, we need a new time and memory measurement method. The performance of a computer is determined by its specifications such as CPU clock speed and operating system. We can tell the computer performance by its specifications. However, besides CPU clock speed and operating system, there are so many other factors that affect computer performance such as temperature, cache size, the program itself, and many other factors. Thus, determining computer performance by its specification is very hard and not feasible to do.

@@

In this work, we compare contestant's solution and jury's solution. Contestant's solution considered satisfying the problem constraints when the memory and CPU usage of contestant's solution not exceeding jury's solution. Sometimes, contestant solution's memory or CPU exceeds the jury's solution a little bit because of the different implementation. We add a tolerance factor ($\gamma$) to tolerate this problem. Contestant's solution is considered satisfies problem constraints when the Equation \ref{tolerance-factor} is fulfilled. When evaluating contestant's solution, the worker compiles and executes contestant's solution and jury's solution. After executing the solutions, the worker compares the memory and CPU usage of the execution and determine whether the contestant's solution satisfies problem constraints.

@@

We need to distribute grading jobs to worker evenly in order to increase grading performance. There are several load balancing methods that we can use to distribute grading jobs evenly. The easiest way to distribute the jobs is by making each contestant to grade their own submissions. In this work, we did not use this method because this method creates security vulnerabilities.

The other way to distribute grading jobs is by using push-based load balancing method. In push-based load balancing, the online judge server chooses the worker to do the grading jobs. By using this method, every contestant does not know which submission they grade, thus can increase system security. To improve system security, we can also grade every submission multiple times. In order to implement this method, we need the status of all workers. This method is pretty hard to implement because we need to poll the worker status periodically and choose the best worker to evaluate the contestants' submissions.

@@

In this work, we use a pull-based load balancing method. By using this method, we do not have to poll the worker status periodically. The worker will poll the jobs from the server periodically and evaluate them when there is a ready job to be evaluated. To improve system security, we grade every submission multiple times. We define a grading size of the system as the number of times we need to grade each submission. Fig. \ref{pull-based-load-balancing} depicts this method mechanism. This work is easier to be implemented than push-based load balancing method and has the same advantages.

@@

In order to isolate the evaluation process, we use containerization method. We compile and execute contestant's submission inside a lightweight container. This container is created by using several Linux features and system calls such as cgroup, namespace, chroot and setrlimit. We use cgroup to monitor and limit the CPU and memory consumption of the running process. The worker kills the program when the CPU or memory usage is exceeding the limit. In order to isolate the host's user, process and network, we use Linux feature called namespace. By using a namespace, the processes inside an isolated environment will not aware of any process, user or network in the outside of its own environment. In order to isolate filesystem of a process, we use the chroot system call. Besides isolating the filesystem, we also need to bring some files from the host environment into an isolated environment. We bring some of the host filesystems into the isolated environment by using the mount system call. We also limit some of processes resources by using the setrlimit system call. By using setrlimit system call, we limit some process resources such as the number of child processes, the stack size, the number of open files and the size of the created file of that process. Fig. \ref{paper-sandbox-activity} depicts how an isolated environment is created.

@@

In order to evaluate contestant's submissions, we need to compile and execute the submitted source code. To compile the source code, we need a specific compiler. Every worker should have the same version of the compiler. The same compiler with different version can produce different output. In order to keep the fairness of the grading process, we need to distribute the same version of the compiler to all workers in the system. In this work, we distribute the compiler in the autograder program to every worker. Every worker compiles the source code inside an isolated filesystem that has been installed with the same version of compilers.

@@

Every worker needs test-cases to evaluate contestant solutions. A test-case is a pair of text files that contain input and output of the problem. Usually, the test-case files are generated by a test-case generator that created by problem setters. The worker evaluates the contestant solution by executing the solution using the input test-case and compare the output with the output test-case. In order to evaluate the contestant solutions, we need to bring the problem test-cases into the worker. To bring the test-cases into the worker is not easy because the test-case file can be a very large file and confidential.

In this work, we do not transfer the raw test-case files to all the workers. Transferring raw test-case files need huge bandwidth and can reduce grading performance. Instead of transferring raw test-case file, we transfer the test-case generator program to generate test-case files. The worker receives the test-case generator source code from the server and compiles it. The compiled test-case generator program then executed to generates input test-case. The worker uses the jury's solution to generates output test-case files. The worker also needs a checker program to compare contestant's output with jury's output. The checker program receives contestant's output and jury's output as its input and gives the verdict of the submission.

In order to hide the test-case information, we encrypt the test-case generator program and the generated test-case files. Even though the test-case is encrypted, the contestants might decrypt it if they know the encryption key. The contestant can attack the autograder program using reverse engineering technique to obtain the encryption key. In this work, we did not handle this problem. Further research is needed to solve this problem.

@@

Because the autograder programs are deployed in the contestants' computers, the contestants can do everything to the program. The contestant can attack the autograder program on their computer. There are many kinds of attacks that the contestant can do such as changing the compiler program, sending the false verdict to the server and refuse to grade other contestants' submissions. In this work, we did not handle this kind of attacks, but there is a way to handle this kind of attacks.

We can prevent a contestant to refuse to do the grading process by monitoring the grading process. When we find out that there is a worker that do not ask for a job for a long time or do not send the grading result for a long time, we can tell that there is a contestant that attacks the autograder program in their computer. Then, we can warn or disqualify the contestant for attacking the autograder program.

By grading every submission multiple times, we can prevent a worker from being attacked that cause it gives the wrong verdict after grading. When we grade a submission multiple times and there is a contestant that attacks the autograder in their computer, we can tell by investigating the grading result. If the grading result of a worker is different from the rest of the workers, we can tell that the contestant attacks the autograder program in that worker. Then, we can warn or disqualify that contestant for attacking the autograder program.

There are many more types of attacks that we did not handle in this work such as stealing jury's solution, other contestant's solution, and test-case generator. Even though we did not handle some type of attacks, this system can still work in several competitions such as ACM-ICPC. In ACM-ICPC, every team is given a computer by the juries to solve the problems. The juries can install the autograder program inside contestant's computer using the root user and not giving the root access to the contestant. By using this mechanism, the contestant ca not attack the autograder program inside their computer.

@@

Currently, most of online judge systems use separate computers to work as the worker of autograder. In order to improve the grading performance of grading process, we use contestant's computer to work as the worker of autograder. Fig. \ref{architecture-new} depicts the architecture of the system developed in this work.

We named this system UGrade and implement this by developing five programs, i.e., UGServer, UGDesktop, UGCtl, UGJob, and UGSbox. UGServer handles everything related to competition such as authentication, contest creation, problem creation, etc. We can consider UGServer as a server of all the workers in the system. UGServer stores all the problems, submissions and the grading results. We develop UGServer using Python with Django and use GraphQL for the API. We use Django because of its ease of use.

To create an isolated environment, we create a sandbox utility program called UGSbox. By using UGSbox, one can execute a program inside an isolated environment and limit its resources. We develop UGSbox using Golang because of its ease of use. UGSbox is used by autograder program to compiles and executes the program for the grading process.

In this work, we named the autograder program as UGJob. UGJob asks UGServer for a job and does the grading process. UGJob uses UGSbox to compiles and executes the source code it receives from UGServer. We develop UGJob using Golang because of its ease of use. The UGJob is deployed in every contestants' computers. Every installation of the UGJob is equipped with the same compiler to keep the fairness of the grading process.

@@

The contestants can interact with the system using user interface programs, e.g., UGDesktop and UGCtl. UGDesktop is a graphical user interface program to interact with this system. Every contestant uses UGDesktop to read the problem and submit their solutions. UGDesktop will execute UGJob periodically to grade the available job in the server. UGCtl is a text-based user interface program to interact with this system. Basically, UGDesktop and UGCtl have the same role in this system. We develop UGCtl just to automate the testing process. Fig. \ref{component} depicts the relationship of the components we have developed.

@@

We compare the grading performance between UGrade and DOMJudge. We chose DOMJudge as the comparison because it was the most popular open source online judge system for ICPC competition. We deployed UGrade and DOMJudge in a computer with the same specification. Then we deployed fifteen computers to simulating the contestant actions. For DOMJudge, we deployed two more computers to work as the autograder worker. For UGrade, the fifteen computers worked as workers.

We created a dummy competition with a single problem, e.g., polynomial multiplication. This problem was expected to be solved using $O(N log N)$ solution, but there are many other solutions with different complexity. We use four types of solution to simulating contestant submission. The first and second type of solution have $O(N^2)$ complexity but have a different implementation. The third solution has $O(N^{log_2{3}})$ complexity. The fourth solution has $O(N log N)$ complexity and considered as the correct solution.

@@

The fifteen computers were submitting each type of solution one by one two times. We logged every event that happens on the system and analyzed the result. In this work, we grade every submission multiple times for UGrade system. We tested UGrade nine times using three different grading size, e.g., one, two and five. We calculated the average time to grade a single submission in DOMJudge and UGrade. Table \ref{grading-time} shows the comparison between the average time to grade a single submission in each test. Based on Table \ref{grading-time}, we know that the UGrade grades the submission faster than DOMJudge. We also know that the grading size of UGrade affects the grading performance a little bit. By increasing the grading size of UGrade, we will grade each submission slower because each submission needs to be graded many times when the grading size is high. In the other hand, increasing the grading size will increase the system security because the submission graded in many workers. The juries need to adjust the grading size so it is fast enough to grade a single submission and secure enough to prevent any attacks from contestants.

@@

Based on the development and testing we have done, there are some lessons we learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judges that are currently popular. This performance improvement is caused by the number of the worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes a high number of worker too, so that does not affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduces grading performance but increases system security. The low number of grading size increases grading performance but reduces system security. The juries need to adjust the grading size to achieve the best result.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieves this by comparing the jury's solution and contestant's solution in the same computer.
\end{enumerate}

@@

In this work, we use a pull-based load balancing technique to distribute the grading work to all of the workers. This technique causes UGServer load to become very huge and decrease grading performance. In order to increase the grading performance and reduce the load of UGServer, further research is needed to find another way to do the load balancing process.

>>>>

Currently, almost every competitive programming competition uses online judge system to support the competition and use many computers to run autograder in order to improve grading performance, i.e., the number submissions graded in a certain amount of time. Every computer that runs autograder is called a worker. Even though autograder deployed in many computers, the grading performance often not enough to evaluate contestant solutions in real-time because the number of contestants is increasing. Furthermore, the number of computers to deploy autograder affect the procurement cost that need to be incurred by the juries. Therefore, a new grading system is needed to increase grading performance without increasing procurement cost that needs to be incurred.

@@

The security aspect need to be considered when developing an autograding system. Competitive programming contestants might submit a source code that contains a dangerous code. According to \cite{wasikojsurvey}, there are several attacks that can be made by contestants, such as submitting compile bomb code, submitting code that destroys the autograder environment and submitting code that access forbidden computer's resource. In order to prevent such things, an autograding system must execute contestant's code in an isolated environment called sandbox.

There are several ways to create an isolated environment such as using virtual machine and containerization. By using a virtual machine, one can create an isolated operating system inside the host computer. The virtual machine uses a hypervisor to emulate computer hardware and run its own operating system. In Linux based operating system, there is a feature called KVM that makes it possible to create hypervisor as a process in Linux \cite{wfeltervmcontainer}. The virtual machine can be used to isolate the execution of contestant's code. However, by using the virtual machine, there is booting process that need to be done everytime contentant's submission is evaluated. This booting process takes so much computer's resource and reduces grading performance.

Another way to create an isolated environment is by using a container. A container is different from a virtual machine. A container gives isolation in software level without any hypervisor \cite{merkeldocker}. By using a container, the execution process can be done without booting a new operating system. The container works by using some Linux features such as chroot, namespace and cgroup. By using chroot, the filesystem of Linux process can be isolated \cite{lessardchroot}. The container uses a Linux feature called cgroup to limit process resources. By using cgroup, the memory usage, CPU usage, and disk IO usage of running process can be limited \cite{wfeltervmcontainer}. In order to hide other processes, user, and network from a running process, the container uses a Linux feature called namespace. By using a namespace, the Linux process can be isolated from from other processes, so the running process will not aware of the existence of other processes. Instead of a virtual machine, most of the autograding systems use container to isolate the grading process. This method was chosen because it is lighter and faster than the virtual machine.

@@

Contestants' computers have different specification and performance. The juries cannot force the contestants to have an identical computer. Thus, a new time and memory measurement method is needed. The performance of a computer can be determined by its specifications such as CPU clock speed and operating system. However, besides CPU clock speed and operating system, there are so many other factors that affect computer performance such as temperature, cache size, the program itself, and many other factors. Thus, determining computer performance by its specification is very hard and not feasible to do.

@@

In this work, the contestant's solution and jury's solution are compared. Contestant's solution is considered satisfying the problem constraints when the memory and CPU usage of contestant's solution is not exceeding jury's solution. Sometimes, contestant solution's memory or CPU exceeds the jury's solution a little bit because of the different implementation. The tolerance factor ($\gamma$) was added to tolerate this problem. Contestant's solution will be considered satisfying problem constraints when the Equation \ref{tolerance-factor} is fulfilled. When evaluating contestant's solution, the worker compils and executs contestant's solution and jury's solution. After executing the solutions, the worker compares the memory and CPU usage of the execution and determine whether the contestant's solution is satisfying problem constraints.

@@

In order to increasing the grading performance, the grading jobs needs to be distributed evenly to the workers. There are several load balancing methods that can be used to distribute grading jobs evenly. The easiest way to distribute the jobs is by making each contestant to grade their own submissions. This method wasn't used in this work because this method creates security vulnerabilities.

The other way to distribute grading jobs is by using push-based load balancing method. In push-based load balancing, the online judge server chooses the worker to do the grading jobs. By using this method, every contestant does not know which submission they grade, thus can increase system security. To improve system security, every submission can be graded multiple times. In order to implement this method, the status of all workers are needed. This method is pretty hard to implement because the load balancer need to poll the worker status periodically and choose the best worker to evaluate the contestants' submissions.

@@

In this work, the pull-based load balancing method was chosen. By using this method, the worker status doesn't need to be polled periodically. The worker polls the jobs from the server periodically and evaluates them when there is a ready job that need to be evaluated. To improve system security, every submission is graded multiple times. A grading size of the system is defined as the number of second the autograder need to grades each submission. Fig. \ref{pull-based-load-balancing} depicts this method mechanism. This method is easier to be implemented than push-based load balancing method and has the same advantages.

@@

In order to isolate the evaluation process, a containerization method was chosen. The contestant's submission is compiled and executed inside a lightweight container. This container was created by using several Linux features and system calls such as cgroup, namespace, chroot and setrlimit. Cgroup is used to monitor and limit the CPU and memory consumption of the running process. The worker will kill the program when the CPU or memory usage is exceeding the limit. In order to isolate the host's user, process and network, a Linux feature called namespace is used. By using a namespace, the processes inside an isolated environment will not aware of any process, user or network in the outside of its own environment. In order to isolate the filesystem of a process, the chroot system call is used. Besides isolating the filesystem, some files from the host environment are also need to be brought into the isolated environment. Some of the host filesystems are brought into the isolated environment by using the mount system call. Some of processes resources are also limited by using the setrlimit system call. By using setrlimit system call, some process resources are limited such as the number of child processes, the stack size, the number of open files and the size of the created file of that process. Fig. \ref{paper-sandbox-activity} depicts how an isolated environment is created.

@@

In order to evaluated contestant's submissions, The submitted source code needs to be compiled and executed. A specific compiler is needed to compiles the source codes. Every worker should have the same version of the compiler. The same compiler with different version can produce different output. In order to keep the fairness of the grading process, the same version of the compiler needs to be distributed to all workers in the system. In this work, the compiler was installed in the autograder program and distributed to every worker. Every worker compiles the source code inside an isolated filesystem that has been installed with the same version of compilers.

@@

Every worker needs test-cases to evaluate contestant solutions. A test-case is a pair of text files that contain input and output of the problem. Usually, the test-case files are generated by a test-case generator that has been created by the problem setters. The worker evaluates the contestant solution by executing the solution using the input test-case and compare the output with the output test-case. In order to evaluate the contestant solutions, the problem test-cases need to be brought into the worker. Bringing the test-cases into the worker is not easy because the test-case file can be a very large file and confidential.

In this work, the raw test-case is not transferred to all the workers. Transferring raw test-case files needs a huge bandwidth and can reduce grading performance. Instead of transferring raw test-case file, the test-case generator program is transferred to generate test-case files. The worker receives the test-case generator source code from the server and compiles it. The compiled test-case generator program then executed to generates input test-case. The worker uses the jury's solution to generates output test-case files. The worker also needs a checker program to compare contestant's output with jury's output. The checker program receives contestant's output and jury's output as its input and gives the verdict of the submission.

In order to hide the test-case information, the test-case generator program and the generated test-case files is encrypted. Even though the test-case is encrypted, the contestants might decrypt it if they know the encryption key. The contestant can attack the autograder program using reverse engineering technique to obtain the encryption key. In this work, this problem wasn't handled. Further research is needed to solve this problem.

@@

Because the autograder programs are deployed in the contestants' computers, the contestants can do everything to the program. The contestant can attack the autograder program on their computer. There are many kinds of attacks that the contestant can do such as changing the compiler program, sending the false verdict to the server and refusing to grade other contestants' submissions. In this work, this kind of attacks weren't handled, but there is a way to handle this kind of attacks.

The autograder can prevent a contestant to refuse to do the grading process by monitoring the grading process. When it finds out that there is a worker that do not ask for a job for a long time or do not send the grading result for a long time, it can tells that there is a contestant that attacks the autograder program in their computer. Then, it can warns or disqualify the contestant for attacking the autograder program.

By grading every submission multiple times, a worker can be prevented from being attacked that cause it gives the wrong verdict after grading. When the autograder grades a submission multiple times and there is a contestant that attacks the autograder in their computer, it can tell by investigating the grading result. If the grading result of a worker is different from the rest of the workers, it can tell that the contestant is attacking the autograder program in that worker. Then, it can warn or disqualify that contestant for attacking the autograder program.

There are many more types of attacks that weren't handled in this work such as stealing jury's solution, other contestant's solution, and test-case generator. Even though that problems were not handle some type of attacks, this system can still work in several competitions such as ACM-ICPC. In ACM-ICPC, every team is given a computer by the juries to solve the problems. The juries can install the autograder program inside contestant's computer using the root user and not giving the root access to the contestant. By using this mechanism, the contestant cannot attack the autograder program inside their computer.

@@

Currently, most of online judge systems use separate computers to work as the worker of autograder. In order to improve the grading performance of the grading process, the contestant's computer is used as the worker of autograder. Fig. \ref{architecture-new} depicts the architecture of the system developed in this work.

This system was named UGrade and implemented by developing five programs, i.e., UGServer, UGDesktop, UGCtl, UGJob, and UGSbox. UGServer handles everything related to competition such as authentication, contest creation, problem creation, etc. UGServer can be considered as a server of all the workers in the system. UGServer stores all the problems, submissions and the grading results. UGServer was developed using Python with Django and use GraphQL for the API. Django was used because of its ease of use.

To create an isolated environment, a sandbox utility program called UGSbox was created. By using UGSbox, one can execute a program inside an isolated environment and limit its resources. UGSbox was developed using Golang because of its ease of use. UGSbox is used by autograder program to compiles and executes the program for the grading process.

In this work, the autograder program was named UGJob. UGJob asks UGServer for a job and does the grading process. UGJob uses UGSbox to compiles and executes the source code it receives from UGServer. UGJob was developed using Golang because of its ease of use. The UGJob is deployed in every contestants' computers. Every installation of the UGJob is equipped with the same compiler to keep the fairness of the grading process.

@@

The contestants can interact with the system using user interface programs, e.g., UGDesktop and UGCtl. UGDesktop is a graphical user interface program to interact with this system. Every contestant uses UGDesktop to read the problem and submit their solutions. UGDesktop executes UGJob periodically to grade the available job in the server. UGCtl is a text-based user interface program to interact with this system. Basically, UGDesktop and UGCtl have the same role in this system. UGCtl was developed just to automate the testing process. Fig. \ref{component} depicts the relationship of the components that developed in this work.

@@

The grading performance between UGrade and DOMJudge was compared. DOMJudge was choosen as the comparison because it was the most popular open source online judge system for ICPC competition. UGrade and DOMJudge were deployed in a computer with the same specification. Then fifteen computers were deployed to simulating the contestant actions. For DOMJudge, two more computers were deployed to work as the autograder worker. For UGrade, the fifteen computers worked as workers.

A dummy competition was created with a single problem, e.g., polynomial multiplication. This problem was expected to be solved using $O(N log N)$ solution, but there are many other solutions with different complexity. Four types of solution were used to simulating contestant submission. The first and second type of solution have $O(N^2)$ complexity but have a different implementation. The third solution has $O(N^{log_2{3}})$ complexity. The fourth solution has $O(N log N)$ complexity and considered as the correct solution.

@@

The fifteen computers were submitting each type of solution one by one two times. Every event that happens on the system was logged and the result was analyzed. In this work, every submission was graded multiple times for UGrade system. UGrade was tested nine times using three different grading size, e.g., one, two and five. The average time to grade a single submission in DOMJudge and UGrade was calculated. Table \ref{grading-time} shows the comparison between the average time to grade a single submission in each test. Based on Table \ref{grading-time}, it can be known that the UGrade grades the submission faster than DOMJudge. It can also be known that the grading size of UGrade affects the grading performance a little bit. By increasing the grading size of UGrade, each submission would be graded slower because each submission needs to be graded many times when the grading size is high. In the other hand, increasing the grading size will increase the system security because the submission graded in many workers. The juries need to adjust the grading size so it is fast enough to grade a single submission and secure enough to prevent any attacks from contestants.

@@

Based on the development and testing that have been done, there are some lessons that can be learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judges that are currently popular. This performance improvement is caused by the number of the worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes a high number of worker too, so that does not affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduces grading performance but increases system security. The low number of grading size increases grading performance but reduces system security. The juries need to adjust the grading size to achieve the best result.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieves this by comparing the jury's solution and contestant's solution in the same computer.
\end{enumerate}

@@

In this work, a pull-based load balancing technique was used to distribute the grading work to all of the workers. This technique has caused UGServer load to become very huge and decrease grading performance. In order to increase the grading performance and reduce the load of UGServer, further research is needed to find another way to do the load balancing process.
